---
title: "VME Analysis_R manuscript"
author: "Felix Klotzsche, Sven Ohl"
date: "8 6 2021"
output:
  html_document:
    code_folding: hide

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

This file prints relevant statistics and plots of the vMemEcc manuscript. Please note, analyses and plots produced in Python are not included here - but in a separate notebook.

## Init workspace
```{r init, message=FALSE, warning=FALSE, echo=FALSE}

#--------------------------------------------------------------------------
# Run main script for analysis for:
#  vMemEcc
#--------------------------------------------------------------------------

library(here)
library(knitr)



#--------------------------------------------------------------------------
# Define pathes
path_global 	    <- here('../..')
path_r_data       <- file.path(path_global, 'Data/DataR')
path_scripts_sven <- file.path(here('Workflow_Sven', 
                                    'osf_experiment1', 
                                    '_RScripts'))

#--------------------------------------------------------------------------
## load packages
source(here("Utils", "load_packages.R"))
source(here('Utils', 'print_output.R'))
source(file.path(path_scripts_sven,"loadPackages.R"))

#--------------------------------------------------------------------------

#--------------------------------------------------------------------------
## define colors
source(file.path(path_scripts_sven, "loadColors.R"))
#--------------------------------------------------------------------------

#--------------------------------------------------------------------------
## load function to compute confidence intervals
source(file.path(path_scripts_sven,"loadFunctions.R"))
source(file.path(here('Utils', 'load_functions.R')))
#--------------------------------------------------------------------------

#--------------------------------------------------------------------------
## load theme
source(file.path(path_scripts_sven, "loadTheme.R"))
#--------------------------------------------------------------------------

#--------------------------------------------------------------------------
## load data, assign names for columns and define variable type
source(file.path(here('Utils', 'load_data.R')))
#--------------------------------------------------------------------------
```

## Analysis 01: 
Is there an effect of workload or eccentricity on performance in the VSTM task and in the perception task?

### VSTM Task:
```{r, message=FALSE, warning=FALSE}
# VSTM task:
func_analysis_01('experiment')
```


_show source:_ 
```{r, echo=FALSE}
# Code to chunk:
insert_fun("func_analysis_01")
```
```{r func_analysis_01-source, eval = FALSE}
```

### Perception task:
```{r,  message=FALSE, warning=FALSE}
# perceptual Change Detection Task:
func_analysis_01('perception')
```

```{r func_analysis_01-source, eval = FALSE}
```

#--------------------------------------------------------------------------
## Run analysis 02: The influence of Memory Load and Eccentricity on 
##                  change detection performance:
##                  glmer

# VSTM task:
func_analysis_02('experiment', 'c_ResponseCorrect')

# perceptual Change Detection Task:
func_analysis_02('perception', 'c_ResponseCorrect')


#--------------------------------------------------------------------------
## Run analysis 03: Is there an effect of workload or eccentricity on 
##                  RT in the VSTM task and in the perception task?
##                  ANOVA & post hoc t test

# VSTM task:
func_analysis_03('experiment')

# perceptual Change Detection Task:
func_analysis_03('perception')


#--------------------------------------------------------------------------
## Run analysis 04: The influence of Memory Load and Eccentricity on 
##                  reaction time:
##                  glmer

# VSTM task:
func_analysis_04('experiment', 'c_ResponseTime')

# perceptual Change Detection Task:
func_analysis_04('perception', 'c_ResponseTime')


#--------------------------------------------------------------------------
## Run analysis 05: Is there an effect of workload or eccentricity on 
##                  mean CDA amplitude in the VSTM task?
##                  ANOVA & post hoc t test

func_analysis_05()


#--------------------------------------------------------------------------
## Run analysis 06: Is there an effect of workload or eccentricity on 
##                  mean alpha power in the VSTM task?
##                  ANOVA & post hoc t test

# func_analysis_06()


```